### 2019-04-28 monograph/thesis/chapters/introduction.tex
Fixed the usage of - by \hyp{}

\lang{%
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain\hyp{}text' mode. Since for code sharing, it is vital for you
    to use a versioning control system\footnote{\url{http://www.codeservedcold.com/version-control-importance/}}
    which enable project manager\s and
    programmers themselves, take control of their code changes
    \cite{redesignOfGit}. It does allow to easily perform the tracking of code
    changes \cite{gettingProductive} and
    allow you to better understand what each programmer is doing
    every time he formalizes a change in the code through a `commit', as in
    `git' systems for example. \cite{usingSourceControl}
}{%
    Além do mais,
    também tem-se que preocupar como o código será salvo no sistema de arquivos,
    em seu formato de texto pleno.
    Já que para compartilhar código e trabalhar em times de forma eficiente,
    é essential utilizar-se um sistema de
    versionamento\footnote{\url{http://www.codeservedcold.com/version-control-importance/}} que
    permita gerente de projetos e os próprios programadores,
    ter o controle de suas mudanças no código \cite{redesignOfGit}.
    Tal ferramenta deve permitir facilmente realizar o rastreamento
    das mudanças \cite{gettingProductive} e assim,
    permitir que você entenda melhor o que cada programador está fazendo,
    todas as vezes que eles formalizam uma nova alteração no código-fonte,
    por exemplo,
    através de uma `commit' como conhecidas em sistemas `git' \cite{usingSourceControl}.
}

@@

\lang{%
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did \cite{quitDiffCalculating}.
    Hence, if every programmer re\hyp{}writes the history making changes
    like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines. \cite{findingRegressionsInProjects}
}{%
    Estas conclusões devem-se por que ao trabalhar com um sistema de versionamento como `git',
    recomenda-se manter todo o código sobre um único stilo,
    ou aquilo que conhece-se ``Boas Práticas'' colocado como um padrão a todos.
    Segue-se isso devido aos problemas gerado ao permitir
    que cada programador escreva como lhe agrada melhor.
    Se cada um escreve como bem entende,
    irá existir ruídos de formação em abundância espalhados por tudo o código-fonte,
    o quê complicará a revisão de código,
    dificultando entender o que cada programador fez \cite{quitDiffCalculating}.

>>>>

\lang{%
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain\hyp{}text' mode. Since for code sharing, it is vital for you
    to use a versioning control system\footnote{\url{http://www.codeservedcold.com/version-control-importance/}}
    which enable project manager\s and
    programmers themselves, take control of their code changes
    \cite{redesignOfGit}. It does allow to easily perform the tracking of code
    changes \cite{gettingProductive} and
    allow you to better understand what each programmer is doing
    every time he formalizes a change in the code through a `commit', as in
    `git' systems for example. \cite{usingSourceControl}
}{%
    Além do mais,
    também tem\hyp{}se que preocupar como o código será salvo no sistema de arquivos,
    em seu formato de texto pleno.
    Já que para compartilhar código e trabalhar em times de forma eficiente,
    é essential utilizar\hyp{}se um sistema de
    versionamento\footnote{\url{http://www.codeservedcold.com/version-control-importance/}} que
    permita gerente de projetos e os próprios programadores,
    ter o controle de suas mudanças no código \cite{redesignOfGit}.
    Tal ferramenta deve permitir facilmente realizar o rastreamento
    das mudanças \cite{gettingProductive} e assim,
    permitir que você entenda melhor o que cada programador está fazendo,
    todas as vezes que eles formalizam uma nova alteração no código\hyp{}fonte,
    por exemplo,
    através de uma `commit' como conhecidas em sistemas `git' \cite{usingSourceControl}.
}

@@

\lang{%
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did \cite{quitDiffCalculating}.
    Hence, if every programmer re\hyp{}writes the history making changes
    like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines. \cite{findingRegressionsInProjects}
}{%
    Estas conclusões devem\hyp{}se por que ao trabalhar com um sistema de versionamento como `git',
    recomenda\hyp{}se manter todo o código sobre um único stilo,
    ou aquilo que conhece\hyp{}se ``Boas Práticas'' colocado como um padrão a todos.
    Segue\hyp{}se isso devido aos problemas gerado ao permitir
    que cada programador escreva como lhe agrada melhor.
    Se cada um escreve como bem entende,
    irá existir ruídos de formação em abundância espalhados por tudo o código\hyp{}fonte,
    o quê complicará a revisão de código,
    dificultando entender o que cada programador fez \cite{quitDiffCalculating}.
